NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-17 results.tex
added comments for aaa description

\subsection{\texorpdfstring{$\boldsymbol pp\to \gamma\gamma\gamma$}{pp->aaa}}

@@

>>>>

\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\gamma}$}{aaa} production}
\label{sec:results:aaa}

@@

\begin{itemize}
  \item \pT of 3rd photon much softer than 1st and 2nd
  \item EW corrections to \pT of 1st and 2nd photon nearly identical and 
        $\approx -10\%$ at 500\,GeV, 3rd photon almost twice that.
  \item in all cases NLO EW outside LO uncertainty band
  \item NLO QCD dominated by real corrections, i.e.\ additional 
        jet emissions
  \item intensified through opening of new $qg$ channels and large 
        gluon luminosity
  \item can be controlled in fixed-order calculations through jet veto, 
        needs proper multijet merging
  \item because at LO the leading jet needs to be in the opposite 
        hemisphere as the subleading and third leading jet, 
        $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_3}$ 
        exhibit kinematic edges at LO
  \item kinematic conditions relaxed at NLO (both QCD and EW, 
        but QCD dominating), large corrections around those edges, 
        leads to artifacts in multiplicative combination
  \item NLO QCD very similar for $m_{\gamma_1\gamma_2}$ and 
	$m_{\gamma_1\gamma_3}$, $m_{\gamma_2\gamma_3}$ with interesting 
	structure around 80-90\,GeV
  \item $m_{\gamma_1\gamma_2}$ again exhibits small excess at $2m_W$
  \item small positive EW corrections at small $m_{\gamma\gamma}$ 
  \item $\approx -10\%$ at 1\,TeV for all $m_{\gamma\gamma}$ 
  \item NLO EW very similar for all $m_{\gamma\gamma}$ 
\end{itemize}

\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell^+\ell^-}$}{aall} production}
\label{sec:results:aaz}

\subsection{\texorpdfstring{$\boldsymbol{\gamma\gamma\ell\nu}$}{aalnu} production}
\label{sec:results:aaw}

\comment{MS: is that $\ell^+$ or $\ell^-$?}
